---
title: "nmds_community_LTB"
author: "Lukas Bernhardt"
date: "9/4/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load your libraries
```{r}
library(vegan)
library(ggplot2)
library(ggpubr)
library(vegan)
library(vegan)
library(dplyr)
library(ggplot2)
#library(scatterplot3d)
#library(vegan3d)
library(readr)
library(tibble)
library(RVAideMemoire)
#library(vegan3d)
#library(rgl)
#library(plot3D)
library(RColorBrewer)
library(ggrepel)
library(multcomp)
```


-----------------------------------16S Community Analysis--------------------
#import your csv of choice at whatever taxonomic level you desire. Here I am importing csv's of my 16S community data at the OTU level
```{r}
species_cl= read.csv(file.choose(), sep=",", head= TRUE)

head(species_cl)
#breaking up the original data frame to just include the no-till sites, full-till sites at the class level
species_cl_NT <- species_cl[which(species_cl$Tillage == "No-Till"),]

species_cl_FT <- species_cl[which(species_cl$Tillage == "Full-Till"),]
species_cl_FT

#making matrices of just the OTU's in all of the above instances

jst_cl_NT <- as.data.frame(species_cl_NT[,12:ncol(species_cl_NT)])
jst_cl_FT <- as.data.frame(species_cl_FT[,12:ncol(species_cl_FT)])

head(jst_cl)
jst_cl <- as.data.frame(species_cl[,12:ncol(species_cl)])

```
#Rename the factors 
```{r}
species_cl$Pesticide[species_cl$Pesticide==2]<-"PST"
species_cl$Pesticide[species_cl$Pesticide==1]<-"No-PST"
species_cl$Tillage[species_cl$Tillage==1]<-"No-Till"
species_cl$Tillage[species_cl$Tillage==2]<-"Full-Till"
species_cl$AggSize[species_cl$AggSize==1]<-"1mm-2mm"
species_cl$AggSize[species_cl$AggSize==2]<-"0.025mm-1mm"
species_cl$AggSize[species_cl$AggSize==3]<-"<0.025mm"
species_cl$AggSize[species_cl$AggSize==4]<-">2mm"

```
species_cl

#ordering the factors as I want them to appear in my figures
```{r}
head(species_cl)
species_cl$Block <- factor(species_cl$Block, levels= c("1", "2", "3", "4"))
species_cl$Tillage <- factor(species_cl$Tillage, levels= c("No-Till", "Full-Till"))
species_cl$Pesticide <- factor(species_cl$Pesticide, levels= c("No-PST", "PST"))
species_cl$AggSize <- factor(species_cl$AggSize, levels= c("<0.025mm", "0.025mm-1mm", "1mm-2mm", ">2mm"))

species_cl_NT$Block <- factor(species_cl_NT$Block, levels= c("1", "2", "3", "4"))
species_cl_NT$Pesticide <- factor(species_cl_NT$Pesticide, levels= c("No-PST", "PST"))
species_cl_NT$AggSize <- factor(species_cl_NT$AggSize, levels= c("<0.025mm", "0.025mm-1mm", "1mm-2mm", ">2mm"))


species_cl_FT$Block <- factor(species_cl_FT$Block, levels= c("1", "2", "3", "4"))
species_cl_FT$Pesticide <- factor(species_cl_FT$Pesticide, levels= c("No-PST", "PST"))
species_cl_FT$AggSize <- factor(species_cl_FT$AggSize, levels= c("<0.025mm", "0.025mm-1mm", "1mm-2mm", ">2mm"))
```


###-------------------------Community Analysis---------------------------###

####SHANNONS DIVERSITY#### - FT, NT and ALL
```{r}
#checking out shannon's diversity for class and species between no till, full-till seperately and the whole data set

shan_cl_NT <- diversity(jst_cl_NT)
species_cl_NT$cl_shan <- shan_cl_NT
NTshan.anov <- aov(cl_shan ~ AggSize, data = species_cl_NT)
summary(NTshan.anov)


shan_cl_FT <- diversity(jst_cl_FT)
species_cl_FT$cl_shan <- shan_cl_FT
FTshan.anov <- aov(cl_shan ~ Pesticide, data = species_cl_FT)
summary(FTshan.anov)

shan_cl <- diversity(jst_cl)
species_cl$cl_shan <- shan_cl
SPshan.anov <- aov(cl_shan ~ AggSize * Tillage, data = species_cl)
summary(SPshan.anov)
#Shannon diversity is significantly different between aggregate size classes when full-till and no-till plots are combined together into one analysis
```


####NMDS/PERMANOVA#### - ALL - class

#log transforming my bacterial community data and making a distance matrix from the results
#log+1 used because log(0) is undefined 
```{r}
lg_jst_cl <- log1p(jst_cl)
lg_jst_cl <- data.matrix(lg_jst_cl)

cl_bray_dist <- vegdist(jst_cl, method = "bray")

```


#NMDS: with bray curtis distance measure. Performed for multiple axes. axis where stress decreased by >0.05 was retained. Best solution is on three axes
Stress evalution:
<.05 - excellent
.05-.10 - good
.10-.20 - usable, potential to mislead at upper end

#Running NMDS at with different amount of axes to see which one has the best stress (bray curtis distance used)
```{r}
NMDS_lg_cl_1 <- metaMDS(lg_jst_cl, distance = "bray", k= 1, autotransform = FALSE, trymax = 1000)
NMDS_lg_cl_2 <- metaMDS(lg_jst_cl, distance = "bray", k=2, autotransform = FALSE, trymax= 1000)
NMDS_lg_cl_3 <- metaMDS(jst_cl, distance = "bray", k=3, autotransform = FALSE, trymax = 1000)
NMDS_lg_cl_4 <- metaMDS(lg_jst_cl, distance = "bray", k= 4, autotransform = FALSE, trymax = 1000)
NMDS_lg_cl_5 <- metaMDS(lg_jst_cl, distance = "bray", k=5, autotransform = FALSE, trymax = 1000)
NMDS_lg_cl_6 <- metaMDS(lg_jst_cl, distance = "bray", k=6, autotransform = FALSE, trymax = 1000)


#determined 3 axis solution was best
spp_stressvector<-as.vector(c(NMDS_lg_cl_1$stress, NMDS_lg_cl_2$stress, NMDS_lg_cl_3$stress, NMDS_lg_cl_4$stress, NMDS_lg_cl_5$stress, NMDS_lg_cl_6$stress))
plot(spp_stressvector)

#looking at the stress for solutions with axes 2-5
NMDS_lg_cl_2$stress
NMDS_lg_cl_3$stress
NMDS_lg_cl_4$stress
NMDS_lg_cl_5$stress

```
***Adding environmental variables***

#Making environmental matrix should just include the metadata (block, plot etc...) and any other environmental variables of interest (pH, EC, total carbon, etc...)
```{r}
head(species_cl)
env_var <- as.data.frame(species_cl[,1:11])
env_var
```


#extracting the site and species scores from the NMDS for plotting
#Choose which NMDS axis you want to plot and substitute for "NMDS_lg_cl_3"
```{r}
site.scrs <- as.data.frame(scores(NMDS_lg_cl_3, display = "sites"))

#Two ways to accomplish the same thing

site.scrs$AggSize = env_var$AggSize
site.scrs$Tillage = env_var$Tillage
site.scrs$Block = env_var$Block
site.scrs

#Species Scores
spp.scrs <- as.data.frame(scores(NMDS_lg_cl_3, display = "species"))
spp.scrs <- cbind(spp.scrs, Species = row.names(spp.scrs))

spp.scrs
```

```{r}
### First, let's relativize the environmental data. We only actually have one numeric environmental variables, so it is not important in this situation, but when you have several environmental variables, it frequently is. Imagine environmental variables whose units are not comparable (ie. pH, depth of soil horizon, canopy cover, etc.). It is particularly important to standardize such values. The vegan function decostand() is really useful for this purpose! 

env_var

env_var$Block <- as.factor(env_var$Block)
env_var$AggSize <- as.factor(env_var$AggSize)
env_var$Tillage <- as.factor(env_var$Tillage)
env_var$Pesticide <- as.factor(env_var$Pesticide)


env_var_rel_lg <- decostand(select_if(env_var, is.numeric), method = "log")

env_var_rel_fit <- envfit(NMDS_lg_cl_3, env_var_rel_lg, choices = 1:2, permutations = 999)
env.scores <- as.data.frame(scores(env_var_rel_fit, display = "vectors"))
env.scores
env.scores2 <- cbind(env.scores, env.variables = rownames(env.scores), pval = env_var_rel_fit$vectors$pvals)
env.scores2 <- subset(env.scores2, pval<=0.05)
env.scores2
# NMDS_1v2_spp_scrs_with_env
```
***Plotting***

Add sites
```{r}
plot(NMDS_lg_cl_3, "sites")
orditorp(plot(NMDS_lg_cl_3), display="sites", col= "red", air= 0.01)   # Gives points labels

#color by till_treat
NMDS_1v2 <- ggplot(site.scrs, aes(x = NMDS1, y = NMDS2)) + geom_point(aes(NMDS1, NMDS2, shape = Tillage, colour = factor(AggSize)), size = 2.6) + labs(colour = "Aggregate Size Class", shape = "Tillage Treatment") + theme_classic() + theme(legend.title = element_text(size = 10, face = "bold"), legend.text = element_text(size = 8, face = "bold")) + scale_color_manual(values= c("#ffcc00", "#669900", "#663300", "#e60000"))
NMDS_1v2

species_cl


```


#Add environmental variables
```{r}
NMDS_1v2_with_env <- NMDS_1v2 + geom_segment(data = env.scores2, aes(x = 0, xend = NMDS1*0.85, y = 0, yend = NMDS2*0.85), arrow = arrow(length = unit(0.25, "cm")), colour = "grey10", lwd = 0.3) + ggrepel::geom_text_repel(data = env.scores2, aes(x = NMDS1*0.9, y = NMDS2*0.9, label = env.variables), cex = 4, direction = "both", segment.size = 0.25)
NMDS_1v2_with_env                                                                  
ggsave("16S_community_NMDS.png", plot = NMDS_1v2_with_env, dpi = 400, height = 5, width = 7)



```



#Saving figures for publication!
```{r}
NMDS_1v2_with_env
setwd("_______________________")
ggsave("community_class_NMDS.png", plot = NMDS_1v2_with_env, dpi = 400, height = 5, width = 6)

```


By changing NMDS1 and NMDS2, you can make figures for NMDS1 vs. NMDS3 and NMDS2 vs NMDS3

NMDS axis: 
The interpretation of NMDS ordinations is fundementally different than PCA. The first axis in PCA, by definition, always explains the most variation in the data. The second axis explains the second most variation orthoganal to the first axis. NMDS axis should be treated as meaningless. The number of axis is defined by the user, and the algorithm then attempts to reposition the observations in a way that maintains their ranked distances.  


********************************PERMANOVA*********************************************************

```{r}
#Adonis acts on matrices
lg_cl_matrix <- as.matrix(jst_cl)


##makes objects or or vectors of you treatments for use in next step(don't exactly know why I needed to do this but I had to) CHECK FOR YOURSELF!!!
tillage <-as.factor(species_cl$Tillage)
pst<-as.factor(species_cl$Pesticide)
block<-as.factor(species_cl$Block)
agg_class<-as.factor(species_cl$AggSize)

#this is where you actually do the permanovas.  There are slight differences between using "+", "*" or "/" for the interaction effects.  you may need to look into what works well for you if your stuff is factorial (replace ENZdata.M with whatever you called your response matrix).  Do some research on strata= this constrains the permutations and is an important thing to consider. There are also a shitton more options that can be set to check out. there is also an adonis2 but I don't know the difference!!!
adonis(lg_cl_matrix ~ agg_class*tillage, distance="bray", permutations = 999, strata = block)
```

#This does pairwise comparrisons to check for differences withing treatment levels. I checked pairwise to see if there were differences among my size classes or block.  The first line of code here makes a distance matrix using bray curtis distance from my original data matrix

#Bonferroni correction to be conservative and reduce the chance of type 1 error
```{r}
###pairwise comparisons of emergent data
###first we need to create a distance matrix
lg_cl_matrix_B <- vegdist(lg_cl_matrix, distance= "bray")

pairwise.perm.manova(lg_cl_matrix_B, tillage, nperm = 1000, p.method = "bonferroni")
pairwise.perm.manova(lg_cl_matrix_B, block, nperm = 1000, p.method = "bonferroni")
pairwise.perm.manova(lg_cl_matrix_B, agg_class, nperm = 1000, p.method = "bonferroni")
```

**********************************************************************************************************************************************************

####PERMANOVA#### NT

```{r}
#Adonis acts on matrices
lg_cl_NT_matrix <- as.matrix(lg_jst_cl_NT)
str(lg_cl_NT_matrix)
head(lg_cl_NT_matrix)

##makes objects or or vectors of you treatments for use in next step(don't exactly know why I needed to do this but I had to) CHECK FOR YOURSELF!!!
tillage_NT <-as.factor(env_var_NT$Tillage)
pst_NT<-as.factor(env_var_NT$Pesticide)
block_NT<-as.factor(env_var_NT$Block)
agg_class_NT<-as.factor(env_var_NT$AggSize)

#this is where you actually do the permanovas.  There are slight differences between using "+", "*" or "/" for the interaction effects.  you may need to look into what works well for you if your stuff is factorial (replace ENZdata.M with whatever you called your response matrix).  Do some research on strata= this constrains the permutations and is an important thing to consider. There are also a shitton more options that can be set to check out. there is also an adonis2 but I don't know the difference!!!
adonis(lg_cl_NT_matrix ~ agg_class_NT, distance="bray", permutations = 999, strata = block_NT)
```


**********************************************************************************************************************************************************
By changing NMDS1 and NMDS2, you can make figures for NMDS1 vs. NMDS3 and NMDS2 vs NMDS3

NMDS axis: 
The interpretation of NMDS ordinations is fundementally different than PCA. The first axis in PCA, by definition, always explains the most variation in the data. The second axis explains the second most variation orthoganal to the first axis. NMDS axis should be treated as meaningless. The number of axis is defined by the user, and the algorithm then attempts to reposition the observations in a way that maintains their ranked distances.  

####PERMANOVA#### FT

```{r}
#Adonis acts on matrices
lg_cl_FT_matrix <- as.matrix(lg_jst_cl_FT)
str(lg_cl_FT_matrix)
head(lg_cl_FT_matrix)

##makes objects or or vectors of you treatments for use in next step(don't exactly know why I needed to do this but I had to) CHECK FOR YOURSELF!!!
tillage_FT <-as.factor(env_var_FT$Tillage)
pst_FT<-as.factor(env_var_FT$Pesticide)
block_FT<-as.factor(env_var_FT$Block)
agg_class_FT<-as.factor(env_var_FT$AggSize)

#this is where you actually do the permanovas.  There are slight differences between using "+", "*" or "/" for the interaction effects.  you may need to look into what works well for you if your stuff is factorial (replace ENZdata.M with whatever you called your response matrix).  Do some research on strata= this constrains the permutations and is an important thing to consider. There are also a shitton more options that can be set to check out. there is also an adonis2 but I don't know the difference!!!
adonis(lg_cl_FT_matrix ~ agg_class_FT, distance="bray", permutations = 999, strata = block_FT)
```

```{r}
###pairwise comparisons of emergent data
###first we need to create a distance matrix
lg_cl_bray_dist

pairwise.perm.manova(lg_cl_bray_dist_FT, block_FT, nperm = 1000, p.method = "bonferroni")
pairwise.perm.manova(lg_cl_bray_dist_FT, agg_class_FT, nperm = 1000, p.method = "bonferroni")
```

--------------------------------ITS community analysis-----------------------

#Importing Data
```{r}
#import your csv of choice at whatever taxonomic level you desire. Here I am importing csv's of my community data at the level of OTU
species_cl= read.csv(file.choose(), sep=",", head= TRUE)
#making matrices of just the species in all of the above instances
jst_sp <- as.data.frame(species_cl[,12:ncol(species_cl)])

```


#Ordering treatments for ploting
```{r}

species_cl$Block <- factor(species_cl$Block, levels= c("1", "2", "3", "4"))
species_cl$Tillage <- factor(species_cl$Tillage, levels= c("No-Till", "Full-Till"))
species_cl$Pesticide <- factor(species_cl$Pesticide, levels= c("No-PST", "PST"))
species_cl$AggSize <- factor(species_cl$AggSize, levels= c("<0.025mm", "0.025mm-1mm", "1mm-2mm", ">2mm"))
```


###------------------------------------------Community Analysis---------------------------------###

####SHANNONS DIVERSITY#### - FT, NT and ALL
```{r}
shan_cl <- diversity(jst_sp)
species_cl$cl_shan <- shan_cl
SPshan.anov <- aov(cl_shan ~ AggSize * Tillage, data = species_cl)
summary(SPshan.anov)
#Shannon diversity is significantly different between aggregate size classes when full-till and no-till plots are combined together into one analysis
```



#NMDS/PERMANOVA
```{r}
#log transforming my fungal community data and making a distance matrix from the results
lg_jst_cl <- log1p(jst_sp)
lg_jst_cl <- data.matrix(lg_jst_cl)
lg_cl_bray_dist <- vegdist(lg_jst_cl, method = "bray")

```


#NMDS All
Stress evalution:
<.05 - excellent
.05-.10 - good
.10-.20 - usable, potential to mislead at upper end

```{r}
# with bray curtis distance measure. Performed for multiple axes. axis where stress decreased by >0.05 was retained. Best solution is on three axes
NMDS_lg_cl_1 <- metaMDS(lg_jst_cl, distance = "bray", k= 1, autotransform = FALSE, trymax = 1000)
NMDS_lg_cl_2 <- metaMDS(lg_jst_cl, distance = "bray", k=2, autotransform = FALSE, trymax= 1000)
NMDS_lg_cl_3 <- metaMDS(lg_jst_cl, distance = "bray", k=3, autotransform = FALSE, trymax = 1000)
NMDS_lg_cl_4 <- metaMDS(lg_jst_cl, distance = "bray", k= 4, autotransform = FALSE, trymax = 1000)
NMDS_lg_cl_5 <- metaMDS(lg_jst_cl, distance = "bray", k=5, autotransform = FALSE, trymax = 1000)
NMDS_lg_cl_6 <- metaMDS(lg_jst_cl, distance = "bray", k=6, autotransform = FALSE, trymax = 1000)


#determined 3 axis solution was best
spp_stressvector<-as.vector(c(NMDS_lg_cl_1$stress, NMDS_lg_cl_2$stress, NMDS_lg_cl_3$stress, NMDS_lg_cl_4$stress, NMDS_lg_cl_5$stress, NMDS_lg_cl_6$stress))
plot(spp_stressvector)

NMDS_lg_cl_2$stress
NMDS_lg_cl_3$stress
NMDS_lg_cl_4$stress
NMDS_lg_cl_5$stress

NMDS_lg_cl_3
```

#Making environmental matrix
```{r}
head(species_cl)
env_var <- as.data.frame(species_cl[,1:11])
env_var
```


#extracting the site and species scores from the NMDS for plotting
```{r}
site.scrs <- as.data.frame(scores(NMDS_lg_cl_3, display = "sites"))
site.scrs

site.scrs$AggSize = env_var$AggSize
site.scrs$Tillage = env_var$Tillage
site.scrs$Block = env_var$Block
site.scrs$Pesticide = env_var$Pesticide
site.scrs

#Species Scores
spp.scrs <- as.data.frame(scores(NMDS_lg_cl_3, display = "species"))
spp.scrs <- cbind(spp.scrs, Species = row.names(spp.scrs))

```

```{r}
### First, let's relativize the environmental data. We only actually have one numeric environmental variables, so it is not important in this situation, but when you have several environmental variables, it frequently is. Imagine environmental variables whose units are not comparable (ie. pH, depth of soil horizon, canopy cover, etc.). It is particularly important to standardize such values. The vegan function decostand() is really useful for this purpose! 

env_var

env_var$Block <- as.factor(env_var$Block)
env_var$AggSize <- as.factor(env_var$AggSize)
env_var$Tillage <- as.factor(env_var$Tillage)
env_var$Pesticide <- as.factor(env_var$Pesticide)


env_var_rel_lg <- decostand(select_if(env_var, is.numeric), method = "log")

env_var_rel_fit <- envfit(NMDS_lg_cl_3, env_var_rel_lg, choices = 1:2, permutations = 999)
env.scores <- as.data.frame(scores(env_var_rel_fit, display = "vectors"))
env.scores
env.scores2 <- cbind(env.scores, env.variables = rownames(env.scores), pval = env_var_rel_fit$vectors$pvals)
env.scores2 <- subset(env.scores2, pval<=0.05)
env.scores2
# NMDS_1v2_spp_scrs_with_env
```
#Plotting NMDS

```{r}
#add sites to check for visual outliers
plot(NMDS_lg_cl_3, "sites")
orditorp(NMDS_lg_cl_3, display="sites", col= "red", air= 0.01)   # Gives points labels
site.scrs

#color by till_treat
NMDS_1v2 <- ggplot(site.scrs, aes(x = NMDS1, y = NMDS2)) + geom_point(aes(NMDS1, NMDS2, shape = Tillage, colour = factor(AggSize)), size = 2.6) + labs(colour = "Aggregate Size Class", shape = "Tillage Treatment") + theme_classic() + theme(legend.title = element_text(size = 10, face = "bold"), legend.text = element_text(size = 8, face = "bold")) + scale_color_manual(values= c("#ffcc00", "#669900", "#663300", "#e60000"))
NMDS_1v2



```


#Add biplot to NMDS
```{r}
NMDS_1v2_with_env <- NMDS_1v2 + geom_segment(data = env.scores2, aes(x = 0, xend = NMDS1*0.8, y = 0, yend = NMDS2*0.8), arrow = arrow(length = unit(0.25, "cm")), colour = "grey10", lwd = 0.3) + ggrepel::geom_text_repel(data = env.scores2, aes(x = NMDS1*0.9, y = NMDS2*0.9, label = env.variables), cex = 4, direction = "both", segment.size = 0.25)
NMDS_1v2_with_env                                                                                                   


```



#Saving figures for publication!
```{r}
ggsave("ITS_comm_NMDS.png", plot = NMDS_1v2_with_env, dpi = 400, height = 5, width = 6)

```


By changing NMDS1 and NMDS2, you can make figures for NMDS1 vs. NMDS3 and NMDS2 vs NMDS3

NMDS axis: 
The interpretation of NMDS ordinations is fundementally different than PCA. The first axis in PCA, by definition, always explains the most variation in the data. The second axis explains the second most variation orthoganal to the first axis. NMDS axis should be treated as meaningless. The number of axis is defined by the user, and the algorithm then attempts to reposition the observations in a way that maintains their ranked distances.  


********************************PERMANOVA*********************************************************
#Permanova
```{r}
#Adonis acts on matrices
lg_cl_matrix <- as.matrix(lg_jst_cl)
str(lg_cl_matrix)
head(lg_cl_matrix)

##makes objects or or vectors of you treatments for use in next step(don't exactly know why I needed to do this but I had to) CHECK FOR YOURSELF!!!
tillage <-as.factor(species_cl$Tillage)
pst<-as.factor(species_cl$Pesticide)
block<-as.factor(species_cl$Block)
agg_class<-as.factor(species_cl$AggSize)

#this is where you actually do the permanovas.  There are slight differences between using "+", "*" or "/" for the interaction effects.  you may need to look into what works well for you if your stuff is factorial (replace ENZdata.M with whatever you called your response matrix).  Do some research on strata= this constrains the permutations and is an important thing to consider. There are also a shitton more options that can be set to check out. there is also an adonis2 but I don't know the difference!!!
adonis(jst_cl ~ agg_class*tillage*pst, distance="bray", permutations = 999, strata = block)
```

#This does pairwise comparrisons to check for differences withing treatment levels. I checked pairwise to see if there were differences among my size classes or block.  The first line of code here makes a distance matrix using bray curtis distance from my original data matrix


#agg_class
1= 1-2mm
2= 0.025mm- 1mm
3= <0.025 mm
4= >2mm

```{r}
###pairwise comparisons of emergent data
###first we need to create a distance matrix

jst_cl_mat <- as.matrix(jst_cl)
jst_cl_mat_B <- vegdist(jst_cl_mat, method="bray")

pairwise.perm.manova(jst_cl_mat_B, tillage,  nperm = 1000, p.method = "bonferroni")
pairwise.perm.manova(jst_cl_mat_B, block, nperm = 1000, p.method = "bonferroni")
pairwise.perm.manova(jst_cl_mat_B, agg_class, nperm = 1000, p.method = "bonferroni")
pairwise.perm.manova(lg_cl_bray_dist, pst, nperm = 1000, p.method = "bonferroni")
```

******************************************************************************************************************************************************************************************************
***************************************************************************************************


