---
title: "agg_isolation_results"
author: "Lukas Bernhardt"
date: "10/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#This first chunk of code is something that allows the knit to work correctly with Rmarkdown.  I don't know why this is necessary but I should look into this more. you can disregard unless you are trying to make a markdown of this
  
```{r}
r = getOption("repos")
r["CRAN"] = "http://cran.us.r-project.org"
options(repos = r)
```


#Get your libraries set up as needed
```{r}
#Great plotting packages
library(ggplot2)
library(ggpubr)
#vegan is for ecological statistics (multivariate)
library(vegan)
#multiple comparrison statistics (i.e. Tukey tests)
library(multcomp)
library(multcompView)
library(ape)
#dplyr is a data manipulation package
library(dplyr)
#find out what these do
library(car)
library(htmltools)
library(vegan3d)
library(BiodiversityR)
library(RVAideMemoire)
library(dplyr)
```


```{r}
agg_iso= read.csv(file.choose(), sep=",", head= TRUE)
```

```{r}
agg_iso
agg_iso$block <- as.factor(agg_iso$block)
agg_iso$treat <- as.factor(agg_iso$treat)
agg_iso$till_treat <- as.factor(agg_iso$till_treat)
agg_iso$pst_treat <- as.factor(agg_iso$pst_treat)
str(agg_iso)
```



#reordered my treatement data so that when I graph my results, they will appear in this order
```{r}
agg_iso$Treat <- factor(agg_iso$treat, levels= c("1", "2", "3", "4"))
agg_iso$block <- factor(agg_iso$block, levels= c("1", "2", "3", "4"))
agg_iso$till_treat <- factor(agg_iso$till_treat, levels= c("No-Till", "Full-Till"))
agg_iso$pst_treat <- factor(agg_iso$pst_treat, levels= c("No-PST", "PST"))
agg_iso$agg_class <- factor(agg_iso$agg_class, levels= c("<0.25mm", "0.25mm-1mm", "1mm-2mm", ">2mm"))
head(agg_iso)

#agg_iso$agg_class[agg_iso$agg_class=="1mm-2mm"]<-"1mm.2mm"
agg_iso

str(agg_iso)

```


```{r}
# A new matrix was created with the mean and sd by agg_class for total C
agg_prcnt = aggregate(agg_iso$std_prcnt, by = list(agg_iso$agg_class), mean)
# This appended the sd to the existing matrix.
agg_prcnt$sd = aggregate(agg_iso$std_prcnt, by= list(agg_iso$agg_class), sd)[,2]
# Standard error was calculated and appended to the matrix.
agg_prcnt$se = agg_prcnt[,3]/sqrt(16)
agg_prcnt

# A new matrix was created with the mean and sd by agg_class for total C
agg_prcnt_FT = aggregate(agg_iso_FT$std_prcnt, by = list(agg_iso_FT$agg_class), mean)
# This appended the sd to the existing matrix.
agg_prcnt_FT$sd = aggregate(agg_iso_FT$std_prcnt, by= list(agg_iso_FT$agg_class), sd)[,2]
# Standard error was calculated and appended to the matrix.
agg_prcnt_FT$se = agg_prcnt_FT[,3]/sqrt(8)
agg_prcnt_FT

# A new matrix was created with the mean and sd by agg_class for total C
agg_prcnt_NT = aggregate(agg_iso_NT$std_prcnt, by = list(agg_iso_NT$agg_class), mean)
# This appended the sd to the existing matrix.
agg_prcnt_NT$sd = aggregate(agg_iso_NT$std_prcnt, by= list(agg_iso_NT$agg_class), sd)[,2]
# Standard error was calculated and appended to the matrix.
agg_prcnt_NT$se = agg_prcnt_NT[,3]/sqrt(8)
agg_prcnt_NT


```

#splitting up data files into just full till and just no till sites
```{r}
agg_iso
agg_iso_FT <- agg_iso[which(agg_iso$till_treat == "Full-Till"),]
agg_iso_FT
agg_iso_NT <- agg_iso[which(agg_iso$till_treat == "No-Till"),]
agg_iso_NT

```

#anova analying differences between aggregate size classes in just the full till sites
```{r}
# 
prcnt.aov_FT <- aov(std_prcnt ~ agg_class, data = agg_iso_FT)
## Summary of the analysis
summary(prcnt.aov_FT)

TUKEY_prcnt_FT <- TukeyHSD(x = prcnt.aov_FT, 'agg_class', conf.level=0.95)
TUKEY_prcnt_FT
```

#anova analying differences between aggregate size classes in just the no till sites
```{r}
head(agg_iso)
prcnt.aov_NT <- aov(std_prcnt ~ agg_class, data = agg_iso_NT)
## Summary of the analysis
summary(prcnt.aov_NT)

TUKEY_prcnt_NT <- TukeyHSD(x = prcnt.aov_NT, 'agg_class', conf.level=0.95)
TUKEY_prcnt_NT
```

```{r}
# 
prcnt.aov <- aov(std_prcnt ~ agg_class*till_treat, data = agg_iso)
## Summary of the analysis
summary(prcnt.aov)


TUKEY_prcnt <- TukeyHSD(x = prcnt.aov, conf.level=0.95)
TUKEY_prcnt

```



```{r}
my_sum <- agg_iso %>%
  group_by(till_treat) %>%
  summarise( 
    n=8,
    mean=mean(std_prcnt),
    sd=sd(std_prcnt)
  ) %>%
  mutate( se=sd/sqrt(n))  %>%
  mutate( ic=se * qt((1-0.05)/2 + .5, n-1))

agg_summary_NT <- agg_iso_NT %>% # the names of the new data frame and the data frame to be summarised
  group_by(agg_class) %>%   # the grouping variable
  summarise(mean_prcnt = mean(std_prcnt),  # calculates the mean of each group
            sd = sd(std_prcnt), # calculates the standard deviation of each group
            n = n(),  # calculates the sample size per group
            SE = sd(std_prcnt)/sqrt(n())) # calculates the standard error of each group

agg_summary_NT

agg_summary_FT <- agg_iso_FT %>% # the names of the new data frame and the data frame to be summarised
  group_by(agg_class) %>%   # the grouping variable
  summarise(mean_prcnt = mean(std_prcnt),  # calculates the mean of each group
            sd = sd(std_prcnt), # calculates the standard deviation of each group
            n = n(),  # calculates the sample size per group
            SE = sd(std_prcnt)/sqrt(n())) # calculates the standard error of each group

agg_summary_FT


```

#making the bar chart figure
```{r}
agg_bar= read.csv(file.choose(), sep=",", head= TRUE)
agg_bar

agg_bar$mean_prcnt_100 <- agg_bar$mean_prcnt*100

agg_bar$SE_100 <- agg_bar$SE*100

```

```{r}
agg_bar$till_treat <- factor(agg_bar$till_treat, levels= c("No-Till", "Full-Till"))

agg_bar$agg_class <- factor(agg_bar$agg_class, levels= c("<0.25mm", "0.25mm-1mm", "1mm-2mm", ">2mm"))

agg_bar_mic <- agg_iso[which(agg_iso$agg_class == "<0.25mm"),]
agg_bar_sma <- agg_iso[which(agg_iso$agg_class == "0.25mm-1mm"),]
agg_bar_mma <- agg_iso[which(agg_iso$agg_class == "1mm-2mm"),]
agg_bar_lma <- agg_iso[which(agg_iso$agg_class == ">2mm"),]

agg_bar_mic
agg_iso

```


```{r}
agg_bar_mic
# one way anova for microaggregates
aov.mic <- aov(std_100 ~ till_treat, data = agg_bar_mic)
## Summary of the analysis
summary(aov.mic)

aov.sma <- aov(std_100 ~ till_treat, data = agg_bar_sma)
## Summary of the analysis
summary(aov.sma)

aov.mma <- aov(std_100 ~ till_treat, data = agg_bar_mma)
## Summary of the analysis
summary(aov.mma)

aov.lma <- aov(std_100 ~ till_treat, data = agg_bar_lma)
## Summary of the analysis
summary(aov.lma)

```

#Aggregate size class distribution bar chart
```{r}
dodge <- position_dodge(width = 0.9)
limits <- aes(ymax = agg_bar$mean_prcnt_100 + agg_bar$SE_100,
              ymin = agg_bar$mean_prcnt_100 - agg_bar$SE_100)


# Default bar plot
agg_bar_prct<- ggplot(agg_bar, aes(x=till_treat, y=mean_prcnt_100, fill=agg_class)) + 
  geom_bar(stat="identity", color="black", position=position_dodge(0.9)) + geom_errorbar(limits, width=.2, position= position_dodge(0.9)) + scale_fill_manual(values=c("grey95", "grey71","grey53", "grey25")) + theme_classic()

                                                                                      
agg_bar_prct

# Finished bar plot
a <- agg_bar_prct+labs(x="Till Treatment", y = "Aggregate Distribution (%)", legend= "Aggregate Size Class") + guides(fill=guide_legend(title="Aggregate Size Class"))

ggsave("C:/Users/lukas/OneDrive/Desktop/agg_iso_dist.png", plot = a, dpi = 400, height = 7, width = 10)

```
